### 2021-07-05 paper/paper.tex
first edit

\documentclass{juliacon}

%\usepackage{xspace}
\setcounter{page}{1}

%\newcommand{\utd}{\texttt{UnitTestDesign}\xspace}
\newcommand{\utd}{UnitTestDesign}
\begin{document}

@@

\begin{abstract}
The \utd package generates all-pairs test cases for unit tests. It implements a greedy algorithm that minimizes the number of test cases that give $n$-way combinatorial coverage. This library is meant to be convenient to use within Julia's unit testing framework, so you can specify forbidden combinations of arguments, to match the behavior of the function under test.
\end{abstract}

@@

We test code in order to address risk of failure, and we judge risk of failure by the likelihood code will fail, how difficult it is to mitigate a failure, and how important it is to have a correct result. However, whether the result of a calculation matters less than what's in the environment.

Our first unit tests for code often derive from mimicking how a user might write client code. These happy-path tests are narrative. We may augment them with our best guesses for corner cases of a function under test. There are times we want more of a guarantee that a function doesn't have faults. This may be that we recognize the function is complex, or that it's central to a sensitive calculation. We may test a part of a code base well because we want reduce the logical complexity that comes from doubt {cite}.

There is a world of testing tools to help find faults in risky code. Some measure the quality of existing tests. Others select tests to run depending on test coverage or recent code modifications. Let's focus on the first antidote to the biases inherent in narrative testing, those that generate test cases. These are tools that create argument values that you pass into a function under test. Then the author of the test is responsible for checking the validity of the output from the function.

There are a few common strategies for automated test case generation. A randomized approach chooses argument values from the space of allowed arguments, usually with some bias towards choosing possible corner cases. Some tools introduce more structure to choosing random arguments. The \texttt{QuickCheck} and \texttt{Hypothesis} packages use customized generators to create streams of test cases. Concolic testing records the execution of the function under test in order to generate subsequent test cases that are likely to increase line coverage. There are also more mathematical approachses, such as Sobol sequences and orthogonal arrays, which have particular diagnostic uses.

@@

Most of the techniques for test case generation focus more on making a smart set of tests then they focus on making few tests that are of high quality. Combinatorial testing generates fewer tests that are designed to give good branch coverage.

There are two cases where this is crucial. The first is that you have to test a slow function, such as a large, Monte Carlo inference. If the function under test runs for hours or days, then selective testing can respect resource limitations.

The other case is when there is a large test space. We've been talking about a function under test, but this is a stand-in for any test we can parametrize. Let's say we've written an application, that we've unit tested its important supporting functions, and we want to write user-level tests that look for problems from interactions among command-line arguments and choices in parameter files. This can be equivalent to testing a function with twenty or more arguments. Twenty arguments, with four possible values each, would lead to over $10^12$ ways to call this function, so how can we feel our tests begin to cover the problem?

The combinatorial testing in \utd takes the time to optimize the choice of test cases so that they can test the code well. The theory of the game is that each if--then in the code will branch depending on combinations of argument values, so combinatorial testing ensures all combinations of $n$ arguments are tried in at least one test case. Here, $n=2$ for two-way testing, also known as all-pairs testing, but studies have shown that wayness up to $n=6$ can be useful.

In practice, that means that you, the author of the unit test, has to choose a few possible values for each function argument. These values will be samples from equivalence classes for that argument and may include corner cases. Then the \utd library generates a set of test cases. In the unit testing framework, the code loops over the test cases, checking whether the results are acceptable.

While combinatorial testing is a useful tool in some circumstances, there are other tools that generate combinatorial tests. X makes them with a domain-specific language. This company's tool does it.

These companies keep disappearing. The quality of tools is supect (by the authors sometimes). It comes down to an author using the tools available within a framework.

That means the tool has to be usable, too. What happens if we create an all-pairs set of unit tests, but some of them don't work for your function because the combination of arguments doesn't make sense? You have to throw out those tests, but you've lost the very guarantee that this testing method made.
So it has to have a) forbid combinations of argument values, b) n-way testing c) multi-way testing d) start with certain cases.

\section{Solution}

So what we do here: Help anybody do a good job on this algorithm, thanks to some work we did.
Clarify the greedy algorithm. Show the algorithm with its complexity.
Out of scope: advanced data structures, other optimization methods.

An argument is. A value is.

The class of greedy algorithms:
The end result will be a list of test cases that have A columns, where A is the number of arguments.
\begin{enumerate}
   \item Generate a list of all combinations of argument values. For instance, one entry would be that the first value of the second argument must appear with the fourth value of the third argument.
   \item For an n-way coverage algorithm, initialize the first n columns of the test cases with a full factorial set of values.
   \item For each argument from n+1 to A.
   \begin{enumerate}
      \item Grow the test cases wider by finding all cases that match the next empty argument.
      \item Grow the test cases taller by adding a row for all cases that couldn't be matched.
   \end{enumerate}
   \item Fill in any missing values in test cases.
\end{enumerate}

\begin{lstlisting}[language=Julia]
function ipog(arity, n_way)
    nonincreasing = sortperm(arity, rev = true)
    arity = arity[nonincreasing]

@@

If we pick one entry from the proposal and one entry from the test cases, there are five ways they can compare.
\begin{center}
\begin{tabular}{rll}
name & test cases & tuples \\ \hline
ignores & * & * \\
skips & $a$ & * \\
misses & * & $b$ \\
matches & $a$ & $b=a$ \\
mismatches & $a$ & $b\ne a$
\end{tabular}
\end{center}
Only the last comparison is clearly a mismatch.

Let's take two strings of argument values. Each pair of arguments will compare with one of the five ways. If any mismatch, there is a mismatch of the two strings. That leaves several different ways we can call a string matching. We can think of the string as scoring either zero or more than zero ignores, zero or more than zero skips, and so-on. That means there are $2^4-1 = 15$ ways for two strings to match, because nonzero strings will match at least one of the four ways. Which of the 15 ways do we count as a match?

@@

1 and 2 are equivalent when the tuples all have a value in the current column being filled.
For filling the last tests, using no-mismatches works well.

\section{Comparison of Approaches}
to random
to generative

From a user perspective, it's about how easy it is to use one method or another. For instance, QuickCheck does more than generate tests. It reduces the cycle of debugging by finding the simplest test that fails.

to concolic

@@

Unit test is a second telling of a function. A parable.

\input{bib.tex}
\end{document}

>>>>

% JuliaCon proceedings template
\documentclass{juliacon}
\setcounter{page}{1}
\usepackage{xspace}
\newcommand{\utd}{\texttt{UnitTestDesign}\xspace}

\begin{document}

@@

\begin{abstract}

The \utd package generates all-pairs test cases for unit tests. It implements a greedy algorithm that minimizes the number of test cases that give $n$-way combinatorial coverage. This library is meant to be convenient to use within Julia's unit testing framework, so you can specify forbidden combinations of arguments, to match the behavior of the function under test.

\end{abstract}

@@

We test code in order to address risk of failure, and we judge risk of failure by the likelihood code will fail, how difficult it is to mitigate a failure, and how important it is to have a correct result. However, whether the result of a calculation matters less than what's in the environment~\cite{Wiklund2017-ms}.
\vskip 6pt
Our first unit tests for code often derive from mimicking how a user might write client code. These happy-path tests are narrative. We may augment them with our best guesses for corner cases of a function under test. There are times we want more of a guarantee that a function doesn't have faults. This may be that we recognize the function is complex, or that it's central to a sensitive calculation. We may test a part of a code base well because we want reduce the logical complexity that comes from uncertainty~\cite{Sha2001-ie}.

\vskip 6pt
There is a world of testing tools to help find faults in risky code. Some measure the quality of existing tests. Others select tests to run depending on test coverage or recent code modifications. Let's focus on the first antidote to the biases inherent in narrative testing, those that generate test cases.

\vskip 6pt
\begin{lstlisting}[language=Julia]
using UnitTestDesign

@enum Strategy naive keyfitz greville monotonic
arg1 = [1, 4, 8]
arg2 = [:a, :b, :c, :d]
arg3 = [naive, keyfitz, greville, monotonic]
arg4 = ["none", "RK4", "quadrature", "QUADPACK"]
arg5 = [0.0, 9.3, -1.2, Inf]

test_cases = all_pairs(arg1, arg2, arg3, arg4, arg5)
for test_case in test_cases:
    result = samplefunction(test_case...)
    @assert known_invariant(result, test_case)
end
\end{lstlisting}

Here, the \verb|all_pairs| function uses the sample argument values to create a set of test cases. The question is which set of cases it creates and when they are appropriate.

\vskip 6pt
There are a few common strategies for automated test case generation. A randomized approach chooses argument values from the space of allowed arguments, usually with some bias towards choosing possible corner cases~\cite{Lampropoulos2020-sd,Arcuri2012-az}. Some tools introduce more structure to choosing random arguments. The \texttt{QuickCheck} and \texttt{Hypothesis} packages use customized generators to create streams of test cases~\cite{loscher2018automating}. Concolic testing records the execution of the function under test in order to generate subsequent test cases that are likely to increase line coverage~\cite{King1976-jt,Wang2018-xh}. There are also more mathematical approaches, such as Sobol sequences and orthogonal arrays~\cite{He2013-th}, which have particular diagnostic uses.

@@

\vskip 6pt
Most of the techniques for test case generation focus more on making a smart set of tests than they focus on making few tests that are of high quality. Combinatorial testing generates fewer tests that are designed to give good branch coverage~\cite{Nie2011-yl,Grindal2005-su,Kuhn2010-ak}.

\vskip 6pt
There are two cases where this is crucial. The first is that you have to test a slow function, such as a large, Monte Carlo inference. If the function under test runs for hours or days, then selective testing can respect resource limitations.

\vskip 6pt
The other case is when there is a large test space. We've been talking about a function under test, but this is a stand-in for any test we can parametrize. Let's say we've written an application, that we've unit tested its important supporting functions, and we want to write user-level tests that look for problems from interactions among command-line arguments and choices in parameter files. This can be equivalent to testing a function with twenty or more arguments. Twenty arguments, with four possible values each, would lead to over $10^{12}$ ways to call this function, so how can we feel our tests begin to cover the problem?

\vskip 6pt
The combinatorial testing in \utd takes the time to optimize the choice of test cases so that they can test the code well. The theory of the game is that each if--then in the code will branch depending on combinations of argument values, so combinatorial testing ensures all combinations of $n$ arguments are tried in at least one test case. Here, $n=2$ for two-way testing, also known as all-pairs testing, but studies have shown that wayness up to $n=6$ can be useful.

\vskip 6pt
While combinatorial testing is a useful tool in some circumstances, there are other tools that generate combinatorial tests. X makes them with a domain-specific language. This company's tool does it.

\vskip 6pt
These companies keep disappearing. The quality of tools is supect (by the authors sometimes). It comes down to an author using the tools available within a framework.

\vskip 6pt
That means the tool has to be usable, too. What happens if we create an all-pairs set of unit tests, but some of them don't work for your function because the combination of arguments doesn't make sense? You have to throw out those tests, but you've lost the very guarantee that this testing method made.
So it has to have a) forbid combinations of argument values, b) n-way testing c) multi-way testing d) start with certain cases~\cite{Czerwonka2006-hm}.

\section{How to Use Combinatorial Testing}

Depends on what your goals are.
\begin{itemize}
   \item At the top of the stack for comprehensive user-level testing. Here, you use the generator but then write test cases by creating command-line arguments and parameter files. Or you use it to create data sets with the given properties.
   \item 
   \end{itemize}
Do the argument values represent:
\begin{itemize}
   \item Argument values for a function.
   \item Equivalence classes from which to randomly choose values.
   \item Directives on how to make a set of calls to an API.
   \end{itemize}

\vskip 6pt
The person writing the unit tests has to pick the input values. In the same way that you would build up a decision table by selecting values from equivalence classes, you select values here. It can be an advantage in that you control the list and can make it more focused where you expect risk. It can be a disadvantage because your choice could exclude a value that random testing or concolic testing might discover exposes a fault.

\vskip 6pt
There are cases where a function has one argument that is a flag and, when it's chosen, other argument values don't make sense to choose. We want to forbid these from the possible input choices. For instance, if \verb|arg1| can be \verb|true| or \verb|false|, and \verb|arg2| can be \verb|default|, \verb|high|, or \verb|low|, but we want to exclude the combination of \verb|false| and \verb|high| or \verb|low|, then the possible outcomes are \verb|true|-\verb|default|, \verb|true|-\verb|high|, \verb|true|-\verb|low|, \verb|false|-\verb|default|. We can either teach the test generator to forbid two combinations, or we can modify the input values, so that \verb|arg12| represents the four possible cases for \verb|arg1| and \verb|arg2| together.

Forbidden tuples~\cite{Petke2015-ex} for combinatorial testing is a method. Among others~\cite{Grindal2006-vy}.

Mixed-level covering arrays don't have well-understood bounds~\cite{Cohen2003-pg}.

\vskip 6pt
Do the results represent exact values? For mathematical code, we often don't have exact values. You may check the results with
\begin{itemize}
   \item A different version of the same function, some kind of parallel implementation. Could be a more naive algorithm or one that uses a different mathematical representation of the same calculation.
   \item A trait of the result, given the inputs. For instance, it may be that a second execution of the function under test, with the same arguments, modified to have \verb|f(2*a, b/2)=f(a, b)| should give the same result. This is a symmetry test~\cite{Segura2016-qh}.
\end{itemize}

\section{Optimization of Test Cases with Practical Constraints}
Also \textsc{aetg}~\cite{Cohen1997-lb}.

\vskip 6pt
So what we do here: Help anybody do a good job on this algorithm, thanks to some work we did.
Clarify the greedy algorithm~\cite{Lei2008-xt}. Show the algorithm with its complexity.
Out of scope: advanced data structures~\cite{Segall2011-jv}, other optimization methods.

\vskip 6pt
An argument is. A value is.

\vskip 6pt
The class of greedy algorithms:
The end result will be a list of test cases that have A columns, where A is the number of arguments.
\begin{enumerate}
   \item Generate a list of all combinations of argument values. For instance, one entry would be that the first value of the second argument must appear with the fourth value of the third argument.
   \item For an n-way coverage algorithm, initialize the first n columns of the test cases with a full factorial set of values.
   \item For each argument from n+1 to A.
   \begin{enumerate}
      \item Grow the test cases wider by finding all cases that match the next empty argument.
      \item Grow the test cases taller by adding a row for all cases that couldn't be matched.
   \end{enumerate}
   \item Fill in any missing values in test cases.
\end{enumerate}

Higher arity for greedy algorithms is a relatively recent development~\cite{Richard_Kuhn2008-ut}.

\vskip 6pt
\begin{lstlisting}[language=Julia]
function ipog(arity, n_way)
    nonincreasing = sortperm(arity, rev = true)
    arity = arity[nonincreasing]

@@

\vskip 6pt
If we pick one entry from the proposal and one entry from the test cases, there are five ways they can compare.
\begin{center}
\begin{tabular}{rll}
name & test cases & tuples \\ \hline
ignores & * & * \\
skips & $a$ & * \\
misses & * & $b$ \\
matches & $a$ & $b=a$ \\
mismatches & $a$ & $b\ne a$
\end{tabular}
\end{center}
Only the last comparison is clearly a mismatch.

\vskip 6pt
Let's take two strings of argument values. Each pair of arguments will compare with one of the five ways. If any mismatch, there is a mismatch of the two strings. That leaves several different ways we can call a string matching. We can think of the string as scoring either zero or more than zero ignores, zero or more than zero skips, and so-on. That means there are $2^4-1 = 15$ ways for two strings to match, because nonzero strings will match at least one of the four ways. Which of the 15 ways do we count as a match?

@@

\vskip 6pt
1 and 2 are equivalent when the tuples all have a value in the current column being filled.
For filling the last tests, using no-mismatches works well.

\section{Comparison of Approaches}
Classic criticism that coverage shouldn't be your goal~\cite{Inozemtseva2014-gz}. Counterpoint that coverage can be more meaningful for less-used paths in the code~\cite{Cai2005-ex}.

\vskip 6pt
to random
to generative

\vskip 6pt
From a user perspective, it's about how easy it is to use one method or another. For instance, QuickCheck does more than generate tests. It reduces the cycle of debugging by finding the simplest test that fails.

\vskip 6pt
to concolic~\cite{King1976-jt,Wang2018-xh}.

@@

Combinatorial testing can benefit from simulated annealing~\cite{Petke2015-ex}.

Another greedy algorithm~\cite{Calvagna2012-ic,Koc2018-vs}.

This would work well with automated test selection if the the Julia testing framework defined tests such that they could be selected, as is done in X package.

\vskip 6pt
Unit test is a second telling of a function. A parable.

\input{bib.tex}

\end{document}

% Inspired by the International Journal of Computer Applications template
